An HPSG account for verbal reduplication in Mandarin Chinese

### 2023-06-08 chapters/ch02-Phenomenon.tex
Update 2023-06-08-23:44:07

 \citet{Fan1964}, \citet{Arcodiaetal2014}, \citet{MelloniBasciano2018} and \citet{Xie2020} compared the AA, ABAB and AABB forms of reduplication 
and found a number of differences between the AA, ABAB forms compared to the AABB form in terms of their semantics, productivity, syntactic distribution and origin. 
Specifically, \citet{Arcodiaetal2014}, \citet{MelloniBasciano2018} and \citet{Xie2020} identified that AA and ABAB have a diminishing meaning, 
namely that the event happens for a short duration or to a small extent. 
AABB, on the other hand, expresses an increasing meaning, which indicates a repetition or action in progress. 
\citet{Xie2020} also found that AA and ABAB have relatively high productivity, 
whereas the productivity of AABB is low. 
She further showed that AABB is generally correlated with the lack of a postverbal object, but the direct object remains present when a transitive verb undergoes AA or ABAB patterns of reduplication. 
\citet[277]{Fan1964} proposed that AA, ABAB originated from the verb-measure word combination from Middle Chinese, 
while AABB developed from the reiterative rhetoric from Old Chinese. 
These differences seem to suggest that there is a fundmental difference between these two groups of verbal reduplication. 
The current study will only focus on the AA, A-\textit{yi}-A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms of verbal reduplication in Mandarin Chinese.
AA-\textit{kan}, A-\textit{kan}-\textit{kan}, AAB, A-\textit{yi}-AB, A-\textit{le}-AB will also be mentioned occasionally to provide further arguments.
In what follows, the term \textit{reduplication} will be used  to refer specifically to the AA, A\hyp{}-\textit{yi}\hyp{}-A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms, if not specified otherwise.

@@

The reduplication has a \textit{delimitativeness} meaning (e.g. \citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec. 4.3]{XiaoMcEnery2004}). 
To be specific, the reduplication of [$+$durative] verbs reduces the duration of the events,
and the reduplication of [$-$durative] verbs reduces the iteration frequency of the events \citetext{\citealp[14]{Li1996}; \citealp[149--150]{XiaoMcEnery2004}}.
Besides delimitativeness, \citet{Chao1968}, \citet{Fan1964}, \citet{Li1996}, \citet{Smith1991, Smith1994} and \citet{Tsao2001} suggested that the reduplication signifies \textit{tentativeness}, which can be used
``to refer modestly to one's own activities, or for mild imperatives'' \citep[356]{Smith1991}, or ``trying to'' do something \citep[234]{LiThompson1981}.
\textit{Frequentativeness} or \textit{habitualness}, that the event denoted by the verb happens frequently or habitually, is mentioned by \citet{Fan1964}, \citet{Li1996} and \citet{Qian2000} as the meaning of reduplication, as well.
 \citet{Fan1964} further proposed a meaning of \textit{slightness} or \textit{casualness} for reduplication, which implies that the event is unimportant or conveys a casual attitude of the speaker.
 \citet{Zhu1998} suggested that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.

@@

As for A-\textit{yi}-A, \citet[273]{Fan1964} compared examples found in novels and plays and concluded that A-\textit{yi}-A has exactly the same meaning as its AA counterpart.
She thus assumed that AA is merely a form of A-\textit{yi}-A, where the \textit{yi} is omitted phonologically.
\citet{Xing2000} considered that the major  difference in meaning  between AA and A-\textit{yi}-A lies in the speaker's attitude.
The former conveys a casual attitude whereas the latter sounds more serious.
However, he stressed that there is no difference in the delimitative semantics of both forms,
and that the variance in meaning is a pragmatic one.
The difference is also not absolute and often only shows a tendency.
\citet{Xu2002} found out that compared to A-\textit{yi}-A, one tends to use AA in contexts with strong emotional attitudes, urgent, casual, timid or uncertain contexts.
But he also stated that these differences are pragmatic rather than semantic, 
as he argued that AA and A-\textit{yi}-A can be used interchangeably in most cases,
and the specific differences in meaning only arise from specific contexts as a whole.
\citet[15]{Yang2003} suggested that AA and A-\textit{yi}-A have the same core meaning, while A-\textit{yi}-A implies a slightly more serious attitude than AA due to its length.
We assume A-\textit{yi}-A to be a form of reduplication and that it has the same core semantics as AA.

@@

Previous research often claimed that the reduplication can only be used for verb classes of certain \textit{Aktionsarten}, while it is infelicitous for other ones.
\citet[277--278]{Hong1999} and \citet[234--235]{LiThompson1981} suggested that reduplication is only possible for volitional activity verbs.
\citet[70--71]{Dai1997} und \citet[290]{Tsao2001} both considered that reduplication can only be used in dynamic situations.
The former further claimed that achievement verbs cannot be reduplicated.
 \citet[155]{XiaoMcEnery2004}, \citet[20]{Arcodiaetal2014} and \citet{BascianoMelloni2017} proposed that only [$+$dynamic] and [$-$result] verbs can be reduplicated.
This means that the reduplication can only interact with dynamic situations which encode no results and is consequently only compatible with activities and semelfactives, but not with states and achievements.

@@

However, examples such as those in (\ref{ex:redup-achi-stat1}) -- (\ref{ex:redup-achi-stat3}) were found in novels and plays written by native speakers and example sentences like (\ref{ex:redup-achi-stat4}) and (\ref{ex:redup-achi-stat5}) constructed by native speaker linguists.
Here, achievement verbs like \textit{wang} `forget' and \textit{sheng} `give birth to' and stative verbs like \textit{shutan} `be comfortable', \textit{lian'ai} `be in love' and \textit{bing} `be sick' are reduplicated.

@@

\footnotetext[2]{Liu, Zhen. 1963. \textit{Chang chang de liushui [Long long water]}, 72. Beijing: The Writers Publishing House.}
\ea
\ea\label{ex:redup-achi-stat1}
\gll deng ren-men ba zhe jian shi \textit{wang}-\textit{wang} zai shuo ba.\footnotemark\\
wait people-\textsc{pl} \textsc{ba} this \textsc{clf} incident forget-forget then talk \textsc{ptc}\\
\glt `Let's wait until people forget this incident a little bit and then talk about it.'\\

@@

\ex\label{ex:redup-achi-stat5}
\gll jiao ta \textit{sheng-sheng} xiaohai, jiu zhidao zuo muqin de gan-ku le.\\
let she give.birth.to-give.birth.to child then know \textsc{cop} mother \textsc{de} sweet-bitter \textsc{ptc}\\ \jambox{\citep[112]{Chen2005}}
\glt `Let her try to give birth to a child and then she will know the bittersweetness of being a mother.'
\z
\z
\footnotetext[3]{Tian, Han. 1959. \textit{Tianhan xuanji [Selected works of Tianhan]}, 122. Beijing: People's Literature Publishing House.}
\footnotetext[4]{Zhou, Libo. 1958. \textit{Shang xiang ju bian [Big changes of mountains and the countryside]}, 204. Beijing: The Writers Publishing House.}

@@

The literature on reduplication makes different assumptions on whether it is a morphological or syntactic phenomenon.
\citet[Ch. 4]{Chao1968}, \citet[Ch. 3]{LiThompson1981} and \citet[4--5]{Liao2014} listed reduplication under morphological processes. 
\citet{Arcodiaetal2014}, \citet{Xiong2016}, \citet{BascianoMelloni2017}, \citet{YangWei2017}, \citet{MelloniBasciano2018}, \citet{Xie2020},   on the other hand, claimed it to be syntactic.
%And e.g. \citet{Chen2001}, \citet{Chen2005}  and \citet{Yang2003} did not make any claim about its grammatical status.
This section reviews the arguments in \citet{Xie2020}, applies the tests proposed by \citet{Duanmu1998} and \citet{Schaefer2009} to distinguish words from phrases in Mandarin Chinese 
and compares the behaviors of the reduplication with those of Parallel Verb Compounds 
(compounds which consist of two verbs that ``either are synonymous or signal the same type of predicative notions'' \citep[68]{LiThompson1981}, e.g. \textit{gou-mai} `purchase-buy, buy') and {SVC}s. 
The results argue for a morphological status of reduplication.

@@

The first syntactic test is phrasal extension, namely the addition of optional elements \citetext{\citealp[150]{Duanmu1998}; \citealp[280]{Schaefer2009}}. 
Optional elements that can possibly appear in a phrase should be able to be added into it,
and subparts of a phrase should be able to be modified separately. 
If the unit is a word, however, then neither of these should  be possible.
As illustrated in (\ref{ex:forms-mono})--(\ref{ex:forms-vo}) in \sectref{sec:forms}, the reduplication can only be separated by \textit{le} and \textit{yi}. 
As mentioned above, whether aspect markers are considered to be morphological or syntactic elements depends on the theoretical framework (and possibly the target language).\footnote{For example, \citet[Sec. 3.3.1]{Huangetal2009} and \citet[246]{MuellerLipenkova2013} considered the postverbal aspect markers (\textit{-le}, \textit{-zhe} and \textit{-guo}) in Mandarin Chinese to be morphological elements. E.g. \citet{Travis2000, Arcodiaetal2014, BascianoMelloni2017} considered all aspect information to be syntactically encoded.} 
And the status of \textit{yi} is unclear, since it does not carry any additional meaning or grammatical function in the structure. % (more on this topic see Section \ref{sec:jackendoff}).
Turning to separate modification,  the element in the reduplication cannot be modified individually. 
Compared to (\ref{ex:ext-redup1}), where the adverbial \textit{qingsheng de} `quietly' modifies the whole reduplication, (\ref{ex:ext-redup2}) is ungrammatical, 
as the adverbial cannot modify the second element in the reduplication alone.
It is worth mentioning that in (\ref{ex:ext-redup1}), it is not possible to analyze \textit{qingsheng de} `quietly' to modify only the first element in the reduplication, 
because the adverbial does not necessarily occur adjacent to the verb, as in (\ref{ex:ext-redup3}), 
and it still modifies the whole predicate.
(\ref{ex:ext-redup1}) and  (\ref{ex:ext-redup3}) have the same meaning.

>>>>

 \citet{Fan1964}, \citet{Arcodiaetal2014}  and \citet{Xie2020} compared the AA, ABAB and AABB forms of reduplication 
and found a number of differences between the AA, ABAB forms compared to the AABB form in terms of their semantics, productivity, syntactic distribution and origin. 
Specifically, \citet[17--18]{Arcodiaetal2014}, \citet[144]{MelloniBasciano2018} and \citet[90]{Xie2020} identified that AA and ABAB have a diminishing meaning, 
namely that the event happens for a short duration or to a small extent. 
By contrast, AABB expresses an increasing meaning, which indicates a repetition or action in progress. 
\citet[Sec. 3.1]{Xie2020} also found that AA and ABAB have relatively high productivity, 
whereas the productivity of AABB is low. 
She further showed that AABB is generally correlated with the lack of a postverbal object, but the direct object remains present when a transitive verb undergoes AA or ABAB patterns of reduplication. 
\citet[277]{Fan1964} proposed that AA, ABAB originated from the verb-measure word combination from Middle Chinese, 
while AABB developed from the reiterative rhetoric from Old Chinese. 
These differences seem to suggest that there is a fundmental difference between these two groups of verbal reduplication. 
The current study will only focus on the AA, A-\textit{yi}-A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms of verbal reduplication in Mandarin Chinese.
AA-\textit{kan}, A-\textit{kan}-\textit{kan}, AAB, A-\textit{yi}-AB, A-\textit{le}-AB will also be mentioned occasionally to provide further arguments.
In what follows, the term \textit{reduplication} will be used  to refer specifically to the AA, A\hyp{}\textit{yi}\hyp{}A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms, if not specified otherwise.

@@

The reduplication has a \textit{delimitativeness} meaning (e.g. \citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec. 4.3]{XiaoMcEnery2004}). 
To be specific, the reduplication of [$+$durative] verbs reduces the duration of the events,
and the reduplication of [$-$durative] verbs reduces the iteration frequency of the events \citetext{\citealp[14]{Li1996}; \citealp[149--150]{XiaoMcEnery2004}}.
Besides delimitativeness, \citet[204]{Chao1968}, \citet[276]{Fan1964}, \citeauthor{Smith1991} (\citeyear[356]{Smith1991}; \citeyear[199--120]{Smith1994}), \citet[14]{Li1996} and \citet[290--291]{Tsao2001} suggested that the reduplication signifies \textit{tentativeness}, which can be used
``to refer modestly to one's own activities, or for mild imperatives'' \citep[356]{Smith1991}, or ``trying to'' do something \citep[234]{LiThompson1981}.
\textit{Frequentativeness} or \textit{habitualness}, that the event denoted by the verb happens frequently or habitually, is mentioned by \citet[276]{Fan1964}, \citet[15]{Li1996} and \citet[1]{Qian2000} as the meaning of reduplication, as well.
 \citet[276]{Fan1964} further proposed a meaning of \textit{slightness} or \textit{casualness} for reduplication, which implies that the event is unimportant or conveys a casual attitude of the speaker.
 \citet[Sec. 3.1.3]{Zhu1998} suggested that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.

@@

As for A-\textit{yi}-A, \citet[273]{Fan1964} compared examples found in novels and plays and concluded that A-\textit{yi}-A has exactly the same meaning as its AA counterpart.
She thus assumed that AA is merely a form of A-\textit{yi}-A, where the \textit{yi} is omitted phonologically.
\citet[Sec. 5]{Xing2000} considered that the major  difference in meaning  between AA and A-\textit{yi}-A lies in the speaker's attitude.
The former conveys a casual attitude whereas the latter sounds more serious.
However, he stressed that there is no difference in the delimitative semantics of both forms,
and that the variance in meaning is a pragmatic one.
The difference is also not absolute and often only shows a tendency.
\citet{Xu2002} found out that compared to A-\textit{yi}-A, one tends to use AA in contexts with strong emotional attitudes, urgent, casual, timid or uncertain contexts.
But he also stated that these differences are pragmatic rather than semantic, 
as he argued that AA and A-\textit{yi}-A can be used interchangeably in most cases,
and the specific differences in meaning only arise from specific contexts as a whole.
\citet[15]{Yang2003} suggested that AA and A-\textit{yi}-A have the same core meaning, while A-\textit{yi}-A implies a slightly more serious attitude than AA due to its length.
We assume A-\textit{yi}-A to be a form of reduplication and that it has the same core semantics as AA.

@@

Previous research often claimed that the reduplication can only be used for verb classes of certain \textit{Aktionsarten}, while it is infelicitous for other ones.
 \citet[234--235]{LiThompson1981} and \citet[277--278]{Hong1999} suggested that reduplication is only possible for volitional activity verbs.
\citet[70--71]{Dai1997} und \citet[290]{Tsao2001} both considered that reduplication can only be used in dynamic situations.
The former further claimed that achievement verbs cannot be reduplicated.
 \citet[155]{XiaoMcEnery2004}, \citet[20]{Arcodiaetal2014} and \citet[145]{BascianoMelloni2017} proposed that only [$+$dynamic] and [$-$result] verbs can be reduplicated.
This means that the reduplication can only interact with dynamic situations which encode no results and is consequently only compatible with activities and semelfactives, but not with states and achievements.

@@

However, examples such as those in (\ref{ex:redup-achi-stat1}--\subref{ex:redup-achi-stat3}) were found in novels and plays written by native speakers and example sentences like (\ref{ex:redup-achi-stat4}) and (\ref{ex:redup-achi-stat5}) constructed by native speaker linguists.
Here, achievement verbs like \textit{wang} `forget' and \textit{sheng} `give birth to' and stative verbs like \textit{shutan} `be comfortable', \textit{lian'ai} `be in love' and \textit{bing} `be sick' are reduplicated.

@@

\footnotetext[2]{Liu, Zhen. 1963. \textit{Chang chang de liushui [Long long water]}, 72. Beijing: The Writers Publishing House.}
\footnotetext[3]{Tian, Han. 1959. \textit{Tianhan xuanji [Selected works of Tianhan]}, 122. Beijing: People's Literature Publishing House.}
\footnotetext[4]{Zhou, Libo. 1958. \textit{Shang xiang ju bian [Big changes of mountains and the countryside]}, 204. Beijing: The Writers Publishing House.}
%\begin{sloppypar}
\ea
\ea\label{ex:redup-achi-stat1}
\gll deng ren-men ba zhe jian shi \textit{wang}-\textit{wang} zai shuo ba.\footnotemark\\
wait people-\textsc{pl} \textsc{ba} this \textsc{clf} incident forget-forget then talk \textsc{ptc}\\
\glt `Let's wait until people forget this incident a little bit and then talk about it.'\\

@@

\ex\label{ex:redup-achi-stat5}
\gll jiao ta \textit{sheng-sheng} xiaohai, jiu zhidao zuo muqin de gan-ku le.\\
let she give.birth.to-give.birth.to child then know \textsc{cop} mother \textsc{de} sweet-bitter \textsc{ptc}\\ \jambox{\citep[112]{Chen2005}}
\glt `Let her try to give birth to a child and then she will know the bittersweetness of being a mother.'
\z
\z
%\end{sloppypar}

@@

The literature on reduplication makes different assumptions on whether it is a morphological or syntactic phenomenon.
\citet[Ch. 4]{Chao1968}, \citet[Ch. 3]{LiThompson1981} and \citet[4--5]{Liao2014} listed reduplication under morphological processes. 
By contrast, \citet[23]{Arcodiaetal2014}, \citet{Xiong2016}, \citet[146]{BascianoMelloni2017}, \citet[229--231]{YangWei2017}, \citet[330]{MelloniBasciano2018} and \citet{Xie2020}  claimed it to be syntactic.
%And e.g. \citet{Chen2001}, \citet{Chen2005}  and \citet{Yang2003} did not make any claim about its grammatical status.
This section reviews the arguments in \citet{Xie2020}, applies the tests proposed by \citet{Duanmu1998} and \citet{Schaefer2009} to distinguish words from phrases in Mandarin Chinese 
and compares the behaviors of the reduplication with those of Parallel Verb Compounds 
(compounds which consist of two verbs that ``either are synonymous or signal the same type of predicative notions'' \citep[68]{LiThompson1981}, e.g. \textit{gou-mai} `purchase-buy, buy') and {SVC}s. 
The results argue for a morphological status of reduplication.

@@

The first syntactic test is phrasal extension, namely the addition of optional elements \citetext{\citealp[150]{Duanmu1998}; \citealp[280]{Schaefer2009}}. 
Optional elements that can possibly appear in a phrase should be able to be added into it,
and subparts of a phrase should be able to be modified separately. 
If the unit is a word, however, then neither of these should  be possible.
As illustrated in (\ref{ex:forms-mono})--(\ref{ex:forms-vo}) in \sectref{sec:forms}, the reduplication can only be separated by \textit{le} and \textit{yi}. 
As mentioned above, whether aspect markers are considered to be morphological or syntactic elements depends on the theoretical framework (and possibly the target language).\footnote{For example, \citet[Sec. 3.3.1]{Huangetal2009} and \citet[246]{MuellerLipenkova2013} considered the postverbal aspect markers  in Mandarin Chinese (\textit{le}, \textit{zhe} and \textit{guo}) to be morphological elements. E.g. \citet{Travis2000}, \citet{Ramchand2008},  \citet[23]{Arcodiaetal2014}, \citet[146]{BascianoMelloni2017} considered all aspect information to be syntactically encoded.} 
And the status of \textit{yi} is unclear, since it does not carry any additional meaning or grammatical function in the structure. % (more on this topic see Section \ref{sec:jackendoff}).
Turning to separate modification,  the element in the reduplication cannot be modified individually. 
Compared to (\ref{ex:ext-redup1}), where the adverbial \textit{qingsheng de} `quietly' modifies the whole reduplication, (\ref{ex:ext-redup2}) is ungrammatical, 
as the adverbial cannot modify the second element in the reduplication alone.
It is worth mentioning that in (\ref{ex:ext-redup1}), it is not possible to analyze \textit{qingsheng de} `quietly' to modify only the first element in the reduplication, 
because the adverbial does not necessarily occur adjacent to the verb, as in (\ref{ex:ext-redup3}), 
and it still modifies the whole predicate.
(\ref{ex:ext-redup1}) and  (\ref{ex:ext-redup3}) have the same meaning.

### 2023-06-08 chapters/ch04-Previous.tex
Update 2023-06-08-23:44:07

\citet{Fan1964}, \citet{Chao1968} and \citet{Xiong2016} analyzed the reduplication in Mandarin Chinese
as a verbal classifier phrase\footnote{Alternative terms for \textit{verbal classifier}: \textit{measure for verbs of action} in \citet[615]{Chao1968} or \textit{cognate object} in \citet[312]{Chao1968} and  \citet[263]{Hong1999}.
The \textit{verbal classifier phrase}  is also termed \textit{quantity adverbial} in \citet[352--353]{LiThompson1981} or \textit{frequency phrase} in \citet[91]{Huangetal2009}.}.
A verbal classifier is ``a measure for verbs of action expresses the number of times an action takes place” \citep[615]{Chao1968}, such as the \textit{ci} in (\ref{ex:clf}).

@@

 \citet{YangWei2017} endorsed the analysis of  reduplication as an aspect marker following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
 \citet{Tsai2008} provided the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}
He observed that  \textit{zhe} `\textsc{prog}', \textit{le} `\textsc{pfv}' and \textit{wan} `\textsc{compl}' necessarily occur with additional information about the event denoted by the sentence (\ref{ex:incomplete}), 
while \textit{zai} `\textsc{dur}' and \textit{guo} `\textsc{exp}' can occur without further information (\ref{ex:complete}).

@@

Nevertheless, this analysis has some shortcomings.
To begin with, since the combination with aspect markers is completely forbidden, it is impossible for this approach to account for A\hyp{}\textit{le}\hyp{}A.
Moreover, as verbal reduplication is  considered to express a delimitative aspectual meaning,
it seems unconvincing to assume that there is no aspect information in its semantics.
We consider a semantic explanation as described in  \sectref{sec:aspM} to be more reasonable for ruling out aspect markers other than \textit{le}.
Furthermore, this account can only deal with monosyllabic reduplication and handles ABAB and AAB as irregular forms, for the reason that ABAB and AAB reduplication of AB verbs ``are not very productive in Chinese'' \citep[102]{FanSongBond2015}.
This is not true. 
\citet{BascianoMelloni2017}, \citet{MelloniBasciano2018},  \citet{Xing2000stat} and  \citet{Xie2020}  all considered both AA and ABAB to be productive,
and \citet{Xing2000stat} concluded that AAB is productive as well.
Thus, these forms should not be handled as  irregular forms, but should be derivable by lexical rules.

>>>>

\citet{Fan1964}, \citet[205]{Chao1968} and \citet{Xiong2016} analyzed the reduplication in Mandarin Chinese
as a verbal classifier phrase\footnote{Alternative terms for \textit{verbal classifier}: \textit{measure for verbs of action} in \citet[615]{Chao1968} or \textit{cognate object} in \citet[312]{Chao1968} and  \citet[263]{Hong1999}.
The \textit{verbal classifier phrase}  is also termed \textit{quantity adverbial} in \citet[352--353]{LiThompson1981} or \textit{frequency phrase} in \citet[91]{Huangetal2009}.}.
A verbal classifier is ``a measure for verbs of action expresses the number of times an action takes place” \citep[615]{Chao1968}, such as the \textit{ci} in (\ref{ex:clf}).

@@

 \citet[229]{YangWei2017} endorsed the analysis of  reduplication as an aspect marker following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
 \citet{Tsai2008} provided the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}
He observed that  \textit{zhe} `\textsc{prog}', \textit{le} `\textsc{pfv}' and \textit{wan} `\textsc{compl}' necessarily occur with additional information about the event denoted by the sentence (\ref{ex:incomplete}), 
while \textit{zai} `\textsc{dur}' and \textit{guo} `\textsc{exp}' can occur without further information (\ref{ex:complete}).

@@

Nevertheless, this analysis has some shortcomings.
To begin with, since the combination with aspect markers is completely forbidden, it is impossible for this approach to account for A\hyp{}\textit{le}\hyp{}A.
Moreover, as verbal reduplication is  considered to express a delimitative aspectual meaning,
it seems unconvincing to assume that there is no aspect information in its semantics.
We consider a semantic explanation as described in  \sectref{sec:aspM} to be more reasonable for ruling out aspect markers other than \textit{le}.
Furthermore, this account can only deal with monosyllabic reduplication and handles ABAB and AAB as irregular forms, for the reason that ABAB and AAB reduplication of AB verbs ``are not very productive in Chinese'' \citep[102]{FanSongBond2015}.
This is not true. 
\citet[33]{Xing2000stat}, \citet[161]{BascianoMelloni2017}, \citet[329]{MelloniBasciano2018} and  \citet[Sec. 3.1]{Xie2020}  all considered both AA and ABAB to be productive,
and \citet[36]{Xing2000stat} concluded that AAB is productive as well.
Thus, these forms should not be handled as  irregular forms, but should be derivable by lexical rules.

### 2023-06-08 chapters/ch05-Analysis.tex
Update 2023-06-08-23:44:07

Since the above-described lexical rules do not constrain the number of syllables of the input verb, but simply reduplicate its phonology  as a whole,
they can also account for the ABAB and the AB-\textit{le}-AB forms of reduplication,
as long as the input verb is disyllabic.
Notice that  the lexical rules above also produce AB-\textit{yi}-AB and AB\hyp{}\textit{le}\hyp{}\textit{yi}\hyp{}AB for disyllabic input verbs.
Although these forms are generally considered unacceptable \citetext{\citealp[160]{BascianoMelloni2017}, \citealp[275--276]{Hong1999}, \citealp[30]{LiThompson1981}, \citealp[239]{YangWei2017}}, 
\citet[269]{Fan1964} and \citet[143]{Sui2018} considered AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB to be possible, even though they both recognized that these two forms are rare.
Indeed, a few examples of AB\hyp{}\emph{yi}\hyp{}AB and AB\hyp{}\emph{le}\hyp{}\emph{yi}\hyp{}AB in Early Mandarin (12th to 20th centuries) (\ref{ex:AByiAB-lu}--\subref{ex:AByiAB-pu}) and Modern Mandarin (\ref{ex:AByiAB-rou1}--\subref{ex:ABleyiAB-ccl}) were found.

@@

\footnotetext[17]{\textit{Yuanqu xuan: Luzhailang [Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}
\footnotetext[18]{\textit{Yuan Ming juan: Piaotongshi [Yuan and Ming volume: Piaotongshi]}, 308, as cited in \citet[15]{Zhang2000}}
\footnotetext[19]{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
\footnotetext[20]{Li, Jieren. 1962. \textit{Da bo [Great wave]}, vol. 3, 171. Beijing: The Writers Publishing House.}
\begin{sloppypar}
\ea\label{ex:ABleyiAB}
\ea\label{ex:AByiAB-lu}
\gll ni yu wo \textit{zhengli-yi-zhengli}.\footnotemark\\
you let me arrange-one-arrange\\
\glt `Let me arrange it a little bit!'

@@

This suggests that  even though AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB might be degraded, they are not ungrammatical \textit{per se}.
The reason for this degradedness is probably phonological, since AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB contain too many syllables \citetext{\citealp[274]{Fan1964}, \citealp[143]{Sui2018}, \citealp[239]{YangWei2017}, \citealp[15]{Zhang2000}}, but we argue that it is not an issue of grammaticality.
Thus, they can still be produced via the lexical rules posited above, but are ruled out or degraded due to a general phonological constraint.

AAB, A-\textit{yi}-AB, A-\textit{le}-AB, AA-\textit{kan} and A-\textit{kan}-\textit{kan} can also be accounted for by the lexical rules proposed in this section.
They can be analyzed as compounds consisting of a reduplicated monosyllabic verb and another element.
Specifically, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can be considered as the compound of a reduplicated monosyllabic verb (A) and a noun (B).\footnote{
    \citet{Huang1984} and \citet{Her1996, Her2010} argued that some of these V-O combinations are compounds, some are phrases, and some have dual status (both compounds and phrases).
    Following this approach, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can (also) be considered as the phrasal combination of a reduplicated verb and its object.
}
AA-\textit{kan} can be regarded as the compound of a reduplicated monosyllabic verb (A) and the verb \textit{kan} `look',
whereas A-\textit{kan}-\textit{kan} is the compound of a monosyllabic verb (A) and the reduplication of \textit{kan} `look'.
A-\textit{yi}-A-\textit{kan} is also possible, though rare, presumably also due to its length.
An inquiry in CCL found 55 hits of A-\textit{yi}-A-\textit{kan}.
A sample is listed in (\ref{ex:AyiAkan}).

>>>>

Since the above-described lexical rules do not constrain the number of syllables of the input verb, but simply reduplicate its phonology  as a whole,
they can also account for the ABAB and the AB-\textit{le}-AB forms of reduplication,
as long as the input verb is disyllabic.
Notice that  the lexical rules above also produce AB-\textit{yi}-AB and AB\hyp{}\textit{le}\hyp{}\textit{yi}\hyp{}AB for disyllabic input verbs.
Although these forms are generally considered unacceptable \citetext{\citealp[30]{LiThompson1981}; \citealp[275--276]{Hong1999};  \citealp[160]{BascianoMelloni2017}; \citealp[239]{YangWei2017}}, 
\citet[269]{Fan1964} and \citet[143]{Sui2018} considered AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB to be possible, even though they both recognized that these two forms are rare.
Indeed, a few examples of AB\hyp{}\emph{yi}\hyp{}AB and AB\hyp{}\emph{le}\hyp{}\emph{yi}\hyp{}AB in Early Mandarin (12th to 20th centuries) (\ref{ex:AByiAB-lu}--\subref{ex:AByiAB-pu}) and Modern Mandarin (\ref{ex:AByiAB-rou1}--\subref{ex:ABleyiAB-ccl}) were found.

@@

\footnotetext[18]{\textit{Yuanqu xuan: Luzhailang [Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}
\footnotetext[19]{\textit{Yuan Ming juan: Piaotongshi [Yuan and Ming volume: Piaotongshi]}, 308, as cited in \citet[15]{Zhang2000}}
\footnotetext[20]{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
\footnotetext[21]{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
\footnotetext[22]{Li, Jieren. 1962. \textit{Da bo [Great wave]}, 3rd band, 171. Beijing: The Writers Publishing House.}

\begin{sloppypar}
\ea\label{ex:ABleyiAB}
\ea\label{ex:AByiAB-lu}
\gll ni yu wo \textit{zhengli-yi-zhengli}.\footnotemark\\
you let me arrange-one-arrange\\
\glt `Let me arrange it a little bit!'

@@

This suggests that  even though AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB might be degraded, they are not ungrammatical \textit{per se}.
The reason for this degradedness is probably phonological, since AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB contain too many syllables \citetext{\citealp[274]{Fan1964}; \citealp[15]{Zhang2000}; \citealp[239]{YangWei2017}; \citealp[143]{Sui2018}}, but we argue that it is not an issue of grammaticality.
Thus, they can still be produced via the lexical rules posited above, but are ruled out or degraded due to a general phonological constraint.

AAB, A-\textit{yi}-AB, A-\textit{le}-AB, AA-\textit{kan} and A-\textit{kan}-\textit{kan} can also be accounted for by the lexical rules proposed in this section.
They can be analyzed as compounds consisting of a reduplicated monosyllabic verb and another element.
Specifically, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can be considered as the compound of a reduplicated monosyllabic verb (A) and a noun (B).\footnote{
    \citet[64--65]{Huang1984} and \citeauthor{Her1996} (\citeyear[Sec. 2]{Her1996}; \citeyear[Sec. 3.1]{Her2010}) argued that some of these V-O combinations are compounds, some are phrases, and some have dual status (both compounds and phrases).
    Following this approach, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can (also) be considered as the phrasal combination of a reduplicated verb and its object.
}
AA-\textit{kan} can be regarded as the compound of a reduplicated monosyllabic verb (A) and the verb \textit{kan} `look',
whereas A-\textit{kan}-\textit{kan} is the compound of a monosyllabic verb (A) and the reduplication of \textit{kan} `look'.
A-\textit{yi}-A-\textit{kan} is also possible, though rare, presumably also due to its length.
An inquiry in CCL found 55 hits of A-\textit{yi}-A-\textit{kan}.
A sample is listed in (\ref{ex:AyiAkan}).
